Factor Analysis on Report Citations, Using a Combined Latent and logistic Model

### 2019-05-09 Manuscript Tex file/Manuscript/manuscript.tex
Third Upload

\documentclass{article}
\usepackage{mathtools}
\usepackage[nottoc]{tocbibind}
\usepackage[nohead, nomarginpar, margin=1in, foot=.25in]{geometry}
\usepackage{mathtools}
\usepackage{bbm}
\usepackage{amssymb}

@@

@@

\section{ Theoretical Properties }
We are interested in verifying following optimization problem has an unique solution.

\begin{align}
\min\limits_{\alpha \in R, S = S^T \atop L \succ 0}   
-\frac{1}{n} \log \prod_{1\le i< j\le n}\frac{exp\left(X_{ij}\left(\alpha+
L_{ij}+S_{ij}\right)\right)}{1+exp\left(\alpha+
L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
\end{align}

\noindent \textbf{Strong convexity} Denote $L^*$ and $S^*$ as ground truth parameter and let $\theta^*_{ij}=\alpha+L^*_{ij}+S^*_{ij}$, $N=n(n-1)/2$. We can easily check the above logistic likelihood function's Hessian matrix is $N \times N$ diagonal matrix with each entries, $\frac{1}{n}\frac{\exp(\theta^*_{ij})}{(1+\exp(\theta^*_{ij}))^2}$. This means that our likelihood function is strictly convex in a sense that $H \succ 0$, unless $\min_{1\le i< j\le n}\theta^*_{ij}$ tends to $-\infty$. 
This is automatically guaranteed through the construction of our problem, $S_{ij} \in R, S_{ij} \geq 0$, and $L_{ij} = F^T_{i}DF_{j}$.

Once we have the unique $\Theta^* \in R^{n \times n}$, whose each entries are $\theta^*_{ij}$, we further need to confirm if it has an unique decomposition, $\Theta^*=\alpha+L^*+S^*$.
As mentioned in \cite{candes2011robust}, the decomposition is unique, and problem is well posed, as long as the low-rank matrix is not sparse, and vice versa if the sparse component is not low-rank matrix. Specifically, these conditions are guaranteed if the singular vectors of $L^*$ are not sparse and if the non-vanishing entries of $S^*$ occur at random locations. 
It is a natural question whether we can check this kind of incoherence between $L^*$ and $S^*$ by observing the given network data $X$. Since 
$X$ is a drawn data from the probability density, which is characterized by $\Theta^*$ ; $X\sim{P_{\Theta^*}}$,... (To be worked...)

I believe we can establish the the non-asymptotic error bound between optimal estimator and ground truth parameter,
\[
    \|\alpha^*-\hat{\alpha}\|_{F}^{2} + 
    \|M^*-\hat{M}\|_{F}^{2} +
    \|S^*-\hat{S}\|_{F}^{2} \leq  ?
\]

@@

We now present each of the three steps of the ADMM algorithm and show that the proximal
operators $\mathbf{P}_{\lambda,f}$ and $\mathbf{P}_{\lambda,g}$ are easy to evaluate.
Let
$$
x^m = (x^m_\alpha, x^m_M, x^m_L, x^m_S), \quad
z^m = (z^m_\alpha, z^m_M, z^m_L, z^m_S), \quad
u^m = (u^m_\alpha, u^m_M, u^m_L, u^m_S).
$$
Step 1. We solve $x^{m+1} = \mathbf{P}_{\lambda,f}(z^m - u^m)$.
Due to the special structure of $f(\cdot)$,
$x^{m+1}_\alpha, x^{m+1}_M, x^{m+1}_L$, and $x^{m+1}_S$
can be updated separately. More precisely, we have
\begin{eqnarray}
x^{m+1}_\alpha, x^{m+1}_M &=& \mbox{arg min}_{\alpha, M} \quad
-\frac{\alpha}{n} \sum_{1\le i< j\le n}X_{ij}
-\frac{1}{2n} X \bullet M
+ \frac{1}{n} \sum_{1\le i<j\le n} \log \left(1 + e^{\alpha + M_{ij}}\right) \nonumber \\
&& + \frac{1}{2\lambda}\left[\alpha - (z^m_\alpha - u^m_\alpha)\right]^2
+ \frac{1}{2\lambda}\|M - (z^m_M - u^m_M)\|^2_F, \label{eq:admm02} \\
x^{m+1}_L &=& \mbox{arg min}_{ L} \quad \delta \|L\|_\ast
+ \frac{1}{2\lambda}\|L - (z^m_L - u^m_L)\|^2_F,\label{eq:admm03}
\\
&& \mbox{subject to $L$ is positive semidefinite;} \nonumber \\
x^{m+1}_S &=& \mbox{arg min}_{ S} \quad  \gamma \|S\|_1
+ \frac{1}{2\lambda}\|S - (z^m_S - u^m_S)\|^2_F,
\label{eq:admm04}
\\
&& \mbox{subject to $S$ is symmetric,} \nonumber
\end{eqnarray}
where $\|\cdot\|_F$ is the matrix Frobenius norm, defined as
$\|M\|^2_F = \sum_{i,j} m^2_{ij}$ for a matrix $M = (m_{ij})$.
The problem in \eqref{eq:admm02} may not have a closed-form solution. We use a simple gradient descent to solve this step, setting the step size, $\alpha=0.1$ and stopping criteria, $\max(|x_\alpha^{m+1}-x_\alpha^{m}|,\|x_M^{m+1}-x_M^{m}\|_{\infty}) \leq 10^{-9}$. Note that there are close-form solutions to \eqref{eq:admm03} and \eqref{eq:admm04}, while \eqref{eq:admm02} is a unconstrained convex optimization problem. More specifically, in \eqref{eq:admm03}, suppose the eigenvalue decomposition of the symmetric matrix $(z^m_L - u^m_L)$ can be written as
$$
z^m_L - u^m_L = T \Lambda T^T,
$$
where $T$ is orthogonal ($T T^T = I_n$), then, for $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, we have
$$
x^{m+1}_L = J (T \mbox{diag}(\Lambda-\lambda \delta)_+ T^T)J^{T},
$$
and diag$(\Lambda-\lambda \delta)_+$ is a diagonal matrix with the $j$th
diagonal entry being
$$
(\Lambda_{jj}-\lambda \delta)_+ = \left\{
\begin{array}{ll}
0, & \mbox{ if } \Lambda_{jj} < \lambda \delta \\
\Lambda_{jj}-\lambda \delta, & \mbox{ if } \Lambda_{jj} \ge \lambda \delta .
\end{array}
\right.
$$
In \eqref{eq:admm04}, we have, for $i \neq j$,
\[
S_{ij} = \left\{
\begin{array}{ll}
0, & \mbox{ if } |(z^m_S - u^m_S)_{ij}| < \lambda \gamma  \\
(z^m_S - u^m_S)_{ij}-\lambda\gamma , &
\mbox{ if } (z^m_S - u^m_S)_{ij} > \lambda \gamma \\
(z^m_S - u^m_S)_{ij}+\lambda\gamma , &
\mbox{ if } (z^m_S - u^m_S)_{ij} <- \lambda \gamma
\end{array}
\right.
\]
\\

@@

The most important implementation details of this algorithm are the choice of $\lambda$ and stopping criterion. In this work, we simply choose $\lambda = 0.5$. We terminate the algorithm  when in $mth$ iteration, $\|x^{m}_M - x^{m}_L - x^{m}_S\|_F \leq \delta$, with $\delta=10^-7$.

@@

\begin{figure}[!h]
\includegraphics[width=1\textwidth]{Fig1.pdf}
\caption{\it After fitting the model, result of application of $k$-means algorithm on first $K$ eigenvectors of $\hat{L}$ matrix. (Different color represents different clusters of nodes $k$-means assign for three synthetic settings.) }
\label{fig:figure1}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[scale=0.75]{Fig2.pdf}
\caption{\it Edges colored with blue correspond to non-zero entries of estimated $\hat{S}$ matrix. For all three cases, our algorithm correctly separates the "across edges" from edges coming from low-rank matrix structure.}
\end{center}
\label{fig:figure2}
\end{figure}

@@

\subsection{Citation and Co-authorship networks for statisticians }
Recently, Ji and Jin \cite{ji2016coauthorship} published an interesting data set on citation  and co-authorship networks of statisticians. Citation relationship over 3000 papers from 4 statistical journals, published between 2003 and 2012, were collected, and collaborative network between authors of papers is given as well. In this section, we analyze these two networks. \\

@@

\begin{figure}[!h]
\includegraphics[width=1\textwidth]{Fig4.png}
\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network, Co-authorship network.}
\label{fig:figure1}
\end{figure}

@@

\noindent These two topics are classical research topics in field of statistics. Majority of papers in first community study about "Controlling False Discovery Rate" in various statistical settings. Second group talks about "Variable selection" in high-dimensional data. As expected, third group is quite hard to interpret and seems to have substructures. For further investigation on this group, after obtaining the subnetwork which is comprised only with papers in third group, we performed same analysis once again under the assumption that $K=4$. We obtain four subcommunities as follows:

@@

\noindent Out of this one big chunk, we got three small, but meaningful topics: "Bayesian Statistics", "Functional/longitudinal data analysis", "Dimension Reduction". Due to small volume of each communities, we could check that false discoveries for each community are all zero. \\

@@

\begin{figure}[!t]
\includegraphics[width=1\textwidth]{Fig3.eps}
\caption{ From left to right: }
\label{fig:figure1}
\end{figure}

@@

\section{On non-asymptotic error bound of the estimator}
Chen et al. (2016) show that their estimator recovers the algebraic structure, that is, the conditional graph structure and the number of latent variables, with probability tending to one. However, their analysis only allows a growing number of sample points whereas they keep the number of variables fixed. Their result thus severs from the tradition to analyze the more challenging high-dimensional setting, where the number of variables is also explicitly tracked. Our analysis will focus on getting a non-asymptotic error bound of estimator in the context of where the sample size is fixed as 1, and the number of variables is growing. (More detailed descriptions on the differences between Chen et al. (2016) and our model in terms of model formulation is given in Introduction section.) We are interested in solving following optimization problem : 
\begin{equation}\label{eq:1}
\min\limits_{\alpha \in R, S = S^T \atop L \succ 0}   
-\frac{1}{n} \log \prod_{1\le i< j\le n}\frac{exp\left(X_{ij}\left(\alpha+
L_{ij}+S_{ij}\right)\right)}{1+exp\left(\alpha+
L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
\end{equation}

Let ($\hat{\alpha},\hat{L},\hat{S}$) be the solution to (\ref{eq:1}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth which governs the data generating process. Let $\hat{\theta},\theta^{*}$ be defined respectively as, $\hat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\hat{L}+\hat{S}$ and
$\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
And denote the error term for each parameter as $\hat{\Delta}^{\Theta} = \hat{\Theta}-\Theta^{*}, 
\hat{\Delta}^{\alpha} = \hat{\alpha}-\alpha^{*},
\hat{\Delta}^L = \hat{L}-L^{*},
\hat{\Delta}^S = \hat{L}-S^{*}.$
Throughout the proof, let $P=\frac{\exp(\Theta_{ij})}{1+\exp(\Theta_{ij})}$. Moreover, for any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:1})

\[
h(\Theta) = -\frac{1}{n}\sum_{i<j} \Big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \Big\}
\]

Observe that 
$\hat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\hat{L}+\hat{S}$
is an optimal solution to (\ref{eq:1}), and that the ground truth parameter
$\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$ is feasible. Thus, we have the following basic inequality

\begin{equation}\label{eq:2}
    h(\hat{\Theta})-h(\Theta^{*}) 
    + \delta \|\hat{L}\|_\ast + \gamma \|\hat{S}\|_1 
    - \delta \|L^{*}\|_\ast - \gamma \|S^{*}\|_1 \leq 0
\end{equation}

We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of likelihood function is bounded away from zero ($\tau > 0$):  
\[
\nabla^{2}h(\Theta) = diag\Big(vec\Big(\frac{\exp(\Theta)}{(1+\exp(\Theta))^{2}}
\Big)\Big) \succcurlyeq \tau I_{\frac{n(n-1)}{2}\times \frac{n(n-1)}{2}}
\]

For any vector $a$, diag(a) is the diagonal matrix with elements of a on its diagonal. For any square matrix A and B, $ A \succcurlyeq B $ if and only if A-B is positive semi-definite. Through the assumption of strong convexity on $h(\Theta)$, and by the Taylor expansion, we can get a following lower bound on term $h(\hat{\Theta})-h(\Theta^{*})$ :

@@

According to Agarwal et al[2]'s second element of lemma 1, 
the difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\hat{\Delta}^L + L^{*},\hat{\Delta}^S + S^{*})$ is upper-bounded by

@@

To get the further lower bound on trace inner product terms, 
$ \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ $, $ \langle\, \hat\Delta^{L}, \hat\Delta^{S} \rangle\ $, we use a definition of dual norm, and the assumption..., 
\begin{align}
    | \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ |
    &= | \langle\,\hat\Delta^{S},\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ | \\
    &\leq \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \|_{\infty} \|\hat{\Delta}^{S}\|_1 \\
    &\leq (|\hat{\alpha}|+|\alpha^{*}|)\|\hat{\Delta}^{S}\|_1\\
    &\leq 2\kappa\|\hat{\Delta}^{S}\|_1
\end{align}

@@

\begin{align}
    \frac{\tau}{2}\|\hat{\Delta}^{\Theta}\|_{F}^{2} 
    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} 
    - 2\kappa\tau(\frac{n+1}{n})\|\hat{\Delta}^{S}\|_{1} \\
    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} - \frac{\gamma}{2}\|\hat{\Delta}^{S}\|_{1}\\
    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}(\hat{\Delta}^L,\hat{\Delta}^S) \label{eq:26}
\end{align}

>>>>

\documentclass{article}
\usepackage{mathtools}
\usepackage[nottoc]{tocbibind}
\usepackage[nohead, nomarginpar, margin=1in, foot=.25in]{geometry}
\usepackage{mathtools}
\usepackage{bbm}
\usepackage{amssymb}
\usepackage{float}  % For fixing the image in draft

@@

\item To ensure unique separation of $\alpha\mathbbm{1}\mathbbm{1}^T$ and $L$, we assume that eigen-vector of $L$ is centered, that is,
\[
    JLJ = L \quad where \quad
    J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T
\]
This condition uniquely identifies F up to a common orthogonal transformation of its columns.

@@

@@

We now present each of the three steps of the ADMM algorithm and show that the proximal
operators $\mathbf{P}_{\lambda,f}$ and $\mathbf{P}_{\lambda,g}$ are easy to evaluate.
Let
$$
x^m = (x^m_\alpha, x^m_M, x^m_L, x^m_S), \quad
z^m = (z^m_\alpha, z^m_M, z^m_L, z^m_S), \quad
u^m = (u^m_\alpha, u^m_M, u^m_L, u^m_S).
$$
Step 1. We solve $x^{m+1} = \mathbf{P}_{\lambda,f}(z^m - u^m)$.
Due to the special structure of $f(\cdot)$,
$x^{m+1}_\alpha, x^{m+1}_M, x^{m+1}_L$, and $x^{m+1}_S$
can be updated separately. More precisely, we have
\begin{eqnarray}
x^{m+1}_\alpha, x^{m+1}_M &=& \mbox{arg min}_{\alpha, M} \quad
-\frac{\alpha}{n} \sum_{1\le i< j\le n}X_{ij}
-\frac{1}{2n} X \bullet M
+ \frac{1}{n} \sum_{1\le i<j\le n} \log \left(1 + e^{\alpha + M_{ij}}\right) \nonumber \\
&& + \frac{1}{2\lambda}\left[\alpha - (z^m_\alpha - u^m_\alpha)\right]^2
+ \frac{1}{2\lambda}\|M - (z^m_M - u^m_M)\|^2_F, \label{eq:admm02} \\
x^{m+1}_L &=& \mbox{arg min}_{ L} \quad \delta \|L\|_\ast
+ \frac{1}{2\lambda}\|L - (z^m_L - u^m_L)\|^2_F,\label{eq:admm03}
\\
&& \mbox{subject to $L$ is positive semidefinite;} \nonumber \\
x^{m+1}_S &=& \mbox{arg min}_{ S} \quad  \gamma \|S\|_1
+ \frac{1}{2\lambda}\|S - (z^m_S - u^m_S)\|^2_F,
\label{eq:admm04}
\\
&& \mbox{subject to $S$ is symmetric,} \nonumber
\end{eqnarray}
where $\|\cdot\|_F$ is the matrix Frobenius norm, defined as
$\|M\|^2_F = \sum_{i,j} m^2_{ij}$ for a matrix $M = (m_{ij})$.
The problem in \eqref{eq:admm02} may not have a closed-form solution. We use a simple gradient descent to solve this step, setting the step size, $\alpha=0.1$ and stopping criteria, $\max(|x_{\alpha,m}^{(t+1)}-x_{\alpha,m}^{(t)}|,\|x_{M,m}^{(t+1)}-x_{M,m}^{(t)}\|_{\infty}) \leq 10^{-9}$. Note that there are close-form solutions to \eqref{eq:admm03} and \eqref{eq:admm04}, while \eqref{eq:admm02} is a unconstrained convex optimization problem. More specifically, in \eqref{eq:admm03}, suppose the eigenvalue decomposition of the symmetric matrix $(z^m_L - u^m_L)$ can be written as
$$
z^m_L - u^m_L = T \Lambda T^T,
$$
where $T$ is orthogonal ($T T^T = I_n$), then, for $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, we have
$$
x^{m+1}_L = J (T \mbox{diag}(\Lambda-\lambda \delta)_+ T^T)J^{T},
$$
and diag$(\Lambda-\lambda \delta)_+$ is a diagonal matrix with the $j$th
diagonal entry being
$$
(\Lambda_{jj}-\lambda \delta)_+ = \left\{
\begin{array}{ll}
0, & \mbox{ if } \Lambda_{jj} < \lambda \delta \\
\Lambda_{jj}-\lambda \delta, & \mbox{ if } \Lambda_{jj} \ge \lambda \delta .
\end{array}
\right.
$$
In \eqref{eq:admm04}, we have, for $i \neq j$,
\[
S_{ij} = \left\{
\begin{array}{ll}
0, & \mbox{ if } |(z^m_S - u^m_S)_{ij}| < \lambda \gamma  \\
(z^m_S - u^m_S)_{ij}-\lambda\gamma , &
\mbox{ if } (z^m_S - u^m_S)_{ij} > \lambda \gamma \\
(z^m_S - u^m_S)_{ij}+\lambda\gamma , &
\mbox{ if } (z^m_S - u^m_S)_{ij} <- \lambda \gamma
\end{array}
\right.
\]
\\

@@

The most important implementation details of this algorithm are the choice of $\lambda$ and stopping criterion. In this work, we simply choose $\lambda = 0.5$. We terminate the algorithm  when in $mth$ iteration, $\|x^{m}_M - x^{m}_L - x^{m}_S\|_F \leq \delta$, with $\delta=10^{-7}$.

@@

\begin{figure}[h]
\includegraphics[width=1\textwidth]{Fig1.pdf}
\caption{\it After fitting the model, result of application of $k$-means algorithm on first $K$ eigenvectors of $\hat{L}$ matrix. (Different color represents different clusters of nodes $k$-means assign for three synthetic settings.) }
\label{fig:figure1}
\end{figure}

@@

@@

\begin{figure}[b]
\begin{center}
\includegraphics[scale=0.75]{Fig2.pdf}
\caption{\it Edges colored with blue correspond to non-zero entries of estimated $\hat{S}$ matrix. For all three cases, our algorithm correctly separates the "across edges" from edges coming from low-rank matrix structure.}
\end{center}
\label{fig:figure2}
\end{figure}

\subsection{Citation and Co-authorship networks for statisticians }
Recently, Ji and Jin \cite{ji2016coauthorship} published an interesting data set on citation  and co-authorship networks of statisticians. Citation relationship over 3000 papers from 4 statistical journals, published between 2003 and 2012, were collected, and collaborative network between authors of papers is given as well. In this section, we analyze the citation network. \\

@@

@@

\noindent These two topics are classical research topics in field of statistics. First group talks about "Variable selection" in high-dimensional data. Majority of papers in second community study about "Controlling False Discovery Rate" in various statistical settings. As expected, third group is quite hard to interpret and seems to have substructures. For further investigation on this group, after obtaining the sub-network which is comprised only with papers in third group, we performed same analysis once again under the assumption that $K=4$. We obtain four sub-communities as follows:

@@

\begin{figure}[b]
\includegraphics[width=1\textwidth]{Fig4.eps}
\caption{\it Scree plots. From left to right: 543-Citation network, Mixed Topics-Citation network.}
\label{fig:figure4}
\end{figure}

\noindent Out of this one big chunk, we got three small, but meaningful topics: "Bayesian Statistics", "Functional/longitudinal data analysis", "Dimension Reduction". Due to small volume of each communities, we could check that false discoveries for each community are all zero.\\

@@

\begin{figure}[!t]
\includegraphics[width=1\textwidth]{Fig3.eps}
\caption{Illustration of first two eigenvectors of estimated $\hat{L}$ matrix for original
citation network with 543 papers(left) and sub-network graph(right). Presentation
on clustering results of k-means algorithm with different colors.}
\label{fig:figure1}
\end{figure}

@@

\section{ On non-asymptotic error bound of the estimator }
Chen et al.\cite{chen2016fused} show that their estimator recovers the algebraic structure, that is, the conditional graph structure and the number of latent variables, with probability tending to one. However, their analysis only allows a growing number of sample points whereas they keep the number of variables fixed. Their result thus severs from the tradition to analyze the more challenging high-dimensional setting, where the number of variables is also explicitly tracked. Our analysis will focus on getting a non-asymptotic error bound of estimator in the context of where the sample size is fixed as 1, and the number of nodes is growing. Readers can find more detailed descriptions on the differences between Chen et al. \cite{chen2016fused} and our model in terms of model formulation in Introduction section. We are interested in solving following optimization problem :

\begin{equation}\label{eq:1}
\min\limits_{\alpha \in R, S = S^T \atop L \succ 0}   
-\frac{1}{n} \log \prod_{1\le i,j\le n}\frac{exp\left(X_{ij}\left(\alpha+
L_{ij}+S_{ij}\right)\right)}{1+exp\left(\alpha+
L_{ij}+S_{ij}\right)} + \delta \|L\|_\ast + \gamma \|S\|_1
\end{equation}

Astute readers might notice the slight difference of first term in objective function between (\ref{eq:logistic10})
and (\ref{eq:1}). (\ref{eq:1}) sums over the all $(i,j)$ pairs. Due to the symmetry of $X$ and $\Theta=\alpha\mathbbm{1}\mathbbm{1}^T+L+S$, after scaling, the only difference lies in the inclusion of diagonal term of $\Theta$.
It should be noted that this slight modification neither leads to theoretical consequences nor noticeable difference in practice.
Rather, this formulation allows us to simplify the theoretical investigation in a direction to which we want to pursue \cite{ma2017exploration}. Let ($\hat{\alpha},\hat{L},\hat{S}$) be the solution to (\ref{eq:1}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth which governs the data generating process. Let $\hat{\Theta},\Theta^{*}$ be defined respectively as, $\hat{\Theta} = \hat{\alpha}\mathbbm{1}\mathbbm{1}^T+\hat{L}+\hat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
And denote the error term for each parameter as $\hat{\Delta}^{\Theta} = \hat{\Theta}-\Theta^{*}, 
\hat{\Delta}^{\alpha} = \hat{\alpha}-\alpha^{*},
\hat{\Delta}^L = \hat{L}-L^{*},
\hat{\Delta}^S = \hat{S}-S^{*}.$
Throughout the discussion, let $P^{*}=\big\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\big\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$. We impose following assumptions for theoretical guarantees.

\begin{assumption} (\textbf{Strong convexity})
For any $\Theta \in \mathbb{R}^{n\times n}$, define the log-likelihood in (\ref{eq:1}), $h(\Theta) = -\frac{1}{n}\sum_{i,j} \big\{ X_{ij}\Theta_{ij} - \log(1+\exp(\Theta_{ij})) \big\}$.We assume that $h(\Theta)$ is $\tau$-strongly convex in a sense that lowest eigenvalue of Hessian matrix of likelihood function is bounded away from zero ($\tau > 0$):  
\[
\nabla^{2}h(\Theta) = diag\Big(vec\Big(\frac{\exp(\Theta)}{n(1+\exp(\Theta))^{2}}
\Big)\Big) \succcurlyeq \tau I_{n^{2} \times n^{2}}
\]
For any vector $a$, diag(a) is the diagonal matrix with elements of a on its diagonal. For any square matrix A and B, $ A \succcurlyeq B $ if and only if A-B is positive semi-definite.
\end{assumption}

\begin{assumption} (\textbf{Identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, Spikiness of L})
To ensure the identifiability of $\alpha\mathbbm{1}\mathbbm{1}^T$ and L, we assume the latent variables are centered, that is $JL=L$, where $J=I_{n}-\frac{1}{n}\mathbbm{1}\mathbbm{1}^T$, $\mathbbm{1}$ denotes all one vector in $\mathbb{R}^{n}$. We impose a spikiness condition $\|L\|_{\infty}\leq\frac{\kappa}{\sqrt{n \times n}}$ on L, to ensure the separation of L and S matrix \cite{agarwal2012noisy}. We would also note that the constraint $|\alpha|\leq C\kappa$, for an absolute constant $C$, is included partially for obtaining theoretical guarantees.
\end{assumption}

With these assumptions we present the behavior of non-asymptotic error bound of our estimator through following theorem. In our result, we measure error using the squared Frobenius norm summed across both matrices:
\[
    e^{2}(\hat{\alpha}.\hat{L},\hat{S}):=\|\alpha^{*}-\hat{\alpha}\|_{F}^{2} + \|L^{*}-\hat{L}\|_{F}^{2} + \|S^{*}-\hat{S}\|_{F}^{2}
\]

\begin{theorem}
Under the assumptions (4.1) and (4.2),
if we solve the convex problem (\ref{eq:1}) with a pair of regularization parameter $(\delta,\gamma)$ satisfying 
\begin{align}
\delta \geq 4\|\frac{1}{n}(X-P^{*})\|_{op} \quad and \quad \gamma \geq 4\|\frac{1}{n}(X-P^{*})\|_{\infty}+4\kappa\tau\bigg(\frac{Cn+1}{n} \bigg)
\end{align}
There exist universal constants $c_{j}$, j = 1,2,3,  for all integers $k = 1,2,...,n$ and $s = 1,2,...,n^{2}$, where $k = rank(L^{*}), s= |supp(S^{*})|$, we have following upper bound on $e^{2}(\hat{\alpha}.\hat{L},\hat{S})$
\begin{align}
    e^{2}(\hat{\alpha},\hat{L},\hat{S}) \leq
    c_{1}\frac{\delta^{2}}{\tau^{2}} +
    c_{2}\frac{\delta^{2}}{\tau^{2}}
    \bigg\{k + \frac{\tau}{\delta}\sum_{j=k+1}^{n}\sigma_{j}(L^{*})\bigg\} +
    c_{3}\frac{\gamma^{2}}{\tau^{2}}
    \bigg\{s + \frac{\tau}{\gamma}\|S^*_{M^\perp}\|_{1}\bigg\}
\end{align}
\end{theorem}

\begin{proof}
Through the assumption of strong convexity on $h(\Theta)$, and by the Taylor expansion, we can get a following lower bound on term $h(\hat{\Theta})-h(\Theta^{*})$ :

@@

According to Agarwal et al \cite{agarwal2012noisy}'s second element of lemma 1, 
the difference $\mathbb{Q}(L^*,S^*)- \mathbb{Q}(\hat{\Delta}^L + L^{*},\hat{\Delta}^S + S^{*})$ is upper-bounded by

@@

To get the further lower bound on trace inner product terms, 
$ \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \rangle\ $, $ \langle\, \hat\Delta^{L}, \hat\Delta^{S} \rangle\ $, we use a definition of dual norm, and the assumption..., 
\begin{align}
    | \langle\, \hat\Delta^{L} + \hat\Delta^{S} ,\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ |
    &= | \langle\,\hat\Delta^{S},\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T\rangle\ | \\
    &\leq \|\hat{\Delta}^{\alpha}\mathbbm{1}\mathbbm{1}^T \|_{\infty} \|\hat{\Delta}^{S}\|_1 \\
    &\leq (|\hat{\alpha}|+|\alpha^{*}|)\|\hat{\Delta}^{S}\|_1\\
    &\leq 2C\kappa\|\hat{\Delta}^{S}\|_1
\end{align}

@@

\begin{align}
    \frac{\tau}{2}\|\hat{\Delta}^{\Theta}\|_{F}^{2} 
    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} 
    - 2\kappa\tau(\frac{Cn+1}{n})\|\hat{\Delta}^{S}\|_{1} \\
    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} - \frac{\gamma}{2}\|\hat{\Delta}^{S}\|_{1}\\
    &\geq \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}(\hat{\Delta}^L,\hat{\Delta}^S) \label{eq:26}
\end{align}

By combining the relations (\ref{eq:11}) and (\ref{eq:26}), we can get following inequality, 
\[
    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} - \frac{\delta}{2} \mathbb{Q}(\hat{\Delta}^L,\hat{\Delta}^S)\\
    \leq \frac{\delta}{2}\|\hat{\Delta}^{\alpha}\|_{F} + 
    \frac{3\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) +2 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^{*}) + 2\gamma \|S^{*}_{M^\perp}\|_{1}
\]
Further, rearrange the terms, apply triangular inequality, $\mathbb{Q}(\hat{\Delta}^L,\hat{\Delta}^S)\leq \mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + \mathbb{Q}(\hat{\Delta}^L_{B},\hat{\Delta}^S_{M^{\perp}})$, and Agarwal et al[\cite{agarwal2012noisy}]’s third element of lemma 1, we get 
\begin{align}
    \frac{\tau}{2} \|\hat{\Delta}^{\alpha}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{L}\|_{F}^{2} + \frac{\tau}{2} \|\hat{\Delta}^{S}\|_{F}^{2} -
    \frac{\delta}{2}\|\hat{\Delta}^{\alpha}\|_{F} 
    \leq 
    \frac{7\delta}{2}\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) + 4 \delta \sum_{j=k+1}^{n} \sigma_{j}(L^*) + 4\gamma \|S^*_{M^\perp}\|_{1}  \label{eq:42}
\end{align}
Noting that $\hat{\Delta}^{L}_{A}$ has rank at most 2$k$ and that $\hat{\Delta}^{S}_{M}$ lies in the model space $\mathbb{M}$, we find that
\begin{align}
    \delta\mathbb{Q}(\hat{\Delta}^L_{A},\hat{\Delta}^S_{M}) 
    \leq \sqrt{2k}\delta\|\hat{\Delta}^L_{A}\|_{F} + \Psi(\mathbb{M})\gamma\|\hat{\Delta}^S_\mathbb{M}\|_{F}\\
    \leq \sqrt{2k}\delta\|\hat{\Delta}^L\|_{F} + \Psi(\mathbb{M})\gamma\|\hat{\Delta}^S\|_{F} \label{eq:44}
\end{align}
